### 2025-10-16 submissions/03-jpam-RR/submit_journal.tex
Save local work before reconnecting

    \begin{spacing}{\rrxspc}
        \textbf{Response:} I thank the referee for this suggestion. I have added a paragraph in the introduction discussing Telles and Ortiz's Generations of Exclusion and other related works on racial identity and assimilation. Specifically, I add the following paragraph in the introduction: ``While my formal theoretical model provides a logical framework for understanding how bias affects racial identity, the behavioral literature on racial identity and assimilation offers crucial empirical insights that complement this theoretical approach. Research in this tradition emphasizes how racial identity is not merely a cognitive construct but is actively performed, negotiated, and reconstructed through daily interactions and life experiences \autocite{waters1990ethnic}. \textcite{telles2008generations} study of Mexican Americans demonstrates how individuals strategically adapting their racial presentations across different social contexts while maintaining core identity elements across generations. Similarly, behavioral studies have documented how discrimination experiences shape identity salience and group attachment, with individuals developing adaptive strategies that range from ethnic distancing to reactive ethnicity depending on situational factors \autocite{zhou1997segmented}. This behavioral perspective reveals that racial identity operates as both a response to external categorization and an active process of boundary maintenance \autocite{cornell2006ethnicity}. While this literature has primarily relied on qualitative observations and ethnographic methods to document identity flexibility, the present analysis advances this understanding by quantifying these strategic choices through systematic comparison of objective ancestry measures with subjective racial identification across varying environmental contexts.''
    \end{spacing}

@@

    \begin{spacing}{\rrxspc}
        \textbf{Response:} I appreciate the referee's attention to this issue. It is a point I address in the paper's data section in the following footnote ``I restrict first-generation cases to those whose parents were born in Asian countries to exclude US citizens born abroad to American parents''. Following the comment, I added a few sentences to clarify this point. Specifically, I added the following sentences in the data section: ``It is important to note that while the ancestry measure provides an objective assessment of Asian heritage, it may not capture all nuances of racial identity. For instance, White individuals with Asian ancestry born to non-Asian parents in Asia, such as on American military bases, may not be classified as Asian in the data. To avoid potential misclassification, I remove individuals who report that they were born abroad of American parents.''
    \end{spacing}

@@

        I also added the following two discussion of the results in the main text. First: ``I report the results using adult samples in Figure (\ref{plot01-regression-gen-adults}). I present results estimating the main specification for all adults in panel (A) and for first- and second-generation subsamples in panels (B) and (C), respectively. Anti-Asian bias and Asian racial identity reporting exhibit negative associations. One standard deviation anti-Asian bias increases correlate with 5 percentage point decreases in Asian racial identity reporting. Among first-generation Asian American adults, one standard deviation anti-Asian bias increases associate with 2 percentage point decreases in Asian racial identity reporting but is statistically insignificant. Among second-generation Asian American adults, one standard deviation anti-Asian bias increases associate with 13 percentage point decreases in Asian racial identity reporting. '' Second: ``I report the results using adult samples in Figure (\ref{plot01-regression-byparent-adults}). I present results estimating the main specification for all second-generation adults in panel (A) and for AA, AW, and WA children subsamples in panels (B), (C), and (D), respectively. One standard deviation anti-Asian bias increases associate with 13 percentage point decreases in Asian racial identity reporting among second-generation adults. Among second-generation adults with endogamous parents, one standard deviation anti-Asian bias increases associate with 10 percentage point decreases in Asian racial identity reporting but are statistically insignificant. However, one standard deviation anti-Asian bias increases associate with a statistically insignificant 3 percentage point decreases in Asian racial identity reporting among Asian father-White mother adults, and 24 percentage point decreases among White father-Asian mother adults.''
    \end{spacing}

@@

            I present the results in Figures \ref{fig:pp-all-gen}-\ref{fig:marginal-effects-third-grandparental}, reveal that anti-Asian bias significantly decreases the likelihood of reporting ``Asian only'' while increasing the probabilities of both ``White only'' and ``Asian and White/Pacific Islander'' identifications among mixed-ancestry individuals. For example, among second-generation children from Asian father-White mother families, a one standard deviation increase in anti-Asian bias is associated with a 12 percentage point decrease in the probability of reporting ``Asian only,'' a 20 percentage point increase in ``White only,'' and a 5 percentage points decrease in ``Asian and White/Pacific Islander.'' To discuss these results, I broke down the results into two subsection. The first subsection--- sub-section \ref{sec:results-dichotomous} titles ``Dichotomous Asian Racial Identity Reporting and Anti-Asian Bias''---discusses the dichotomous outcomes. The second subsection---sub-section \ref{sec:multinomial} titled ``Multinomial Logit Results: Racial Identity Choices and Anti-Asian Bias''---focuses on the multinomial outcomes.

>>>>

    \begin{spacing}{\rrxspc}
        \textbf{Response:} I thank the referee for this suggestion. I have added a paragraph in the introduction discussing Telles and Ortiz's Generations of Exclusion and other related works on racial identity and assimilation. Specifically, I add the following paragraph in the introduction:

        ``While \textcite{akerlofEconomicsIdentity2000} theoretical model that I use provides a logical framework for understanding how bias affects racial identity, the behavioral literature on racial identity and assimilation offers crucial empirical insights that complement this theoretical approach. Research in this tradition emphasizes how racial identity is not merely a cognitive construct but is actively performed, negotiated, and reconstructed through daily interactions and life experiences \autocite{waters1990ethnic}. \textcite{telles2008generations}'s study of Mexican Americans demonstrates how individuals strategically adapt their racial presentations across different social contexts while maintaining core identity elements across generations.

        Similarly, behavioral studies have documented how discrimination experiences shape identity salience and group attachment, with individuals developing adaptive strategies that range from ethnic distancing to reactive ethnicity depending on situational factors \autocite{zhou1997segmented}. This behavioral perspective reveals that racial identity operates as both a response to external categorization and an active process of boundary maintenance \autocite{cornell2006ethnicity}. While this literature has primarily relied on qualitative observations and ethnographic methods to document identity flexibility, the present analysis advances this understanding by quantifying these strategic choices through systematic comparison of objective ancestry measures with subjective racial identification across varying environmental contexts.''
    \end{spacing}

@@

    \begin{spacing}{\rrxspc}
        \textbf{Response:} I appreciate the referee's attention to this issue. It is a point I address in the paper's data section in the following footnote ``I restrict first-generation cases to those whose parents were born in Asian countries to exclude US citizens born abroad to American parents''. Following the comment, I added a few sentences to clarify this point. Specifically, I added the following sentences in the data section: ``Note that while the ancestry measure provides an objective assessment of Asian heritage, it may not capture all nuances of racial identity. For instance, White individuals with Asian ancestry born to non-Asian parents in Asia, such as on American military bases, may be classified as Asian in the data. To avoid potential misclassification, I remove individuals who report that they were born abroad of American parents.''
    \end{spacing}

@@

        I also added the following two discussion of the results in the main text. First: ``Adult samples show similar patterns (Figure \ref{plot01-regression-gen-adults}).\footnote{For adults with Asian ancestry, I can only observe birthplaces of the person and their parents, not grandparents, limiting analysis to first- and second-generation individuals.} A one standard deviation increase in anti-Asian bias correlates with a 5 percentage point decrease in Asian racial identity reporting across all adults, with a 2 percentage point decrease among first-generation adults (statistically insignificant) and a 13 percentage point decrease among second-generation adults. Higher household income and years of education both positively correlate with Asian identity reporting, with each additional year of education associated with approximately 1--2 percentage point increases.'' Second: ``Adult second-generation results show even larger heterogeneity by family structure (Figure \ref{plot01-regression-byparent-adults}). A one standard deviation increase in anti-Asian bias correlates with a 13 percentage point decrease across all second-generation adults, with the largest effect among White father-Asian mother adults (24 percentage points, panel D). Notably, higher education positively correlates with Asian identity reporting among mixed-race adults but shows no effect in endogamous families, suggesting that more educated individuals with Asian ancestry are more likely to maintain their Asian racial identity. This selective retention implies that studies using self-reported racial identity may overestimate Asian American success and underestimate assimilation speed, as successful Asians remain visible in the data while less successful Asians attrit to other racial categories.''
    \end{spacing}

@@

            I present the results in Figures \ref{fig:pp-all-gen}-\ref{fig:pp-third-three}, reveal that anti-Asian bias significantly decreases the likelihood of reporting ``Asian only'' while increasing the probabilities of both ``White only'' and ``Asian and White/Pacific Islander'' identifications among mixed-ancestry individuals. For example, among second-generation children from Asian father-White mother families, a one standard deviation increase in anti-Asian bias is associated with a 12 percentage point decrease in the probability of reporting ``Asian only,'' a 20 percentage point increase in ``White only,'' and a 5 percentage points decrease in ``Asian and White/Pacific Islander.'' To discuss these results, I broke down the results into two subsection. The first subsection--- sub-section \ref{sec:results-dichotomous} titles ``Dichotomous Asian Racial Identity Reporting and Anti-Asian Bias''---discusses the dichotomous outcomes. The second subsection---sub-section \ref{sec:multinomial} titled ``Multinomial Logit Results: Racial Identity Choices and Anti-Asian Bias''---focuses on the multinomial outcomes.

### 2025-10-16 submissions/03-jpam-RR/tab47-marriage.tex
Save local work before reconnecting

\begin{table}[H]
\centering\centering
\caption{Logistic Regression Analysis of Bias and Interracial Marriages \label{regtab-logit-03}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lccc}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{1}{c}{Asian Men} & \multicolumn{1}{c}{Asian Women} \\
\cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4}
  & \specialcell{(1) \\ Interracial} & \specialcell{(2) \\ Interracial} & \specialcell{(3) \\ Interracial}\\
\midrule
Bias & $1.47$*** & $0.83$ & $1.39$**\\
 & ($0.16$) & ($0.14$) & ($0.20$)\\
College Graduate: Wife & $1.42$*** & $1.55$*** & $1.75$***\\
 & ($0.06$) & ($0.09$) & ($0.09$)\\
College Graduate: Husband & $0.94$ & $0.97$ & $0.86$***\\
 & ($0.04$) & ($0.06$) & ($0.04$)\\
\midrule
Observations & $69,800$ & $52,032$ & $60,171$\\
Year $\times$ Region FE & X & X & X\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{This is the result to estimating (\ref{eq:inter-interracial}) as a
                        logistic regression. The coefficients are exponentiated, thus should be interpreted as odds ratios.}
\item[2] \footnotesize{I include controls for partners' sex, age, education, 
                      and years since immigrating to the United States.
                      Standard errors are clustered on the household level.}
\item[3] \footnotesize{Data source is the 2004-2020 Current Population Survey Data.}
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\begin{table}[H]
\centering\centering
\caption{Logistic Regression Analysis of Bias and Interracial Marriages \label{regtab-logit-03}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lccc}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{1}{c}{Asian Men} & \multicolumn{1}{c}{Asian Women} \\
\cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4}
  & \specialcell{(1) \\ Interethnic} & \specialcell{(2) \\ Interethnic} & \specialcell{(3) \\ Interethnic}\\
\midrule
Bias & $0.38$*** & $-0.19$ & $0.33$**\\
 & ($0.11$) & ($0.16$) & ($0.14$)\\
College Graduate: Wife & $0.35$*** & $0.44$*** & $0.56$***\\
 & ($0.04$) & ($0.06$) & \vphantom{1} ($0.05$)\\
College Graduate: Husband & $-0.06$ & $-0.03$ & $-0.15$***\\
 & ($0.04$) & ($0.06$) & ($0.05$)\\
\midrule
Observations & $69,800$ & $52,032$ & $60,171$\\
Year $\times$ Region FE & X & X & X\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{This is the result to estimating (\ref{eq:inter-interracial}) as a
                        logistic regression. The coefficients are exponentiated, thus should be interpreted as odds ratios.}
\item[2] \footnotesize{I include controls for partners' sex, age, education, 
                      and years since immigrating to the United States.
                      Standard errors are clustered on the household level.}
\item[3] \footnotesize{Data source is the 2004-2020 Current Population Survey Data.}
\end{tablenotes}
\end{threeparttable}
\end{table}
